Deep Learning

### 2015-01-11 deepreview.tex
added caption generation figure, caption, and text

\begin{figure}[ht]
%\centerline{\includegraphics[width=0.7\linewidth]{}}
\caption{Example of captions generated by a recurrent network taking
as extra input the representation extracted by a deep convolutional
net from an image, with the whole system trained to ``translate''
images into captions. Reproduced from~\cite{?}.
}
\label{fig:caption-generation}
\end{figure}

@@

@@

@@

\section{Boxes}

>>>>

\begin{figure}[ht]
\centerline{\includegraphics[width=\linewidth]{caption-generation-Vinyals-et-al.png}}
\caption{Example of captions generated by a recurrent network taking
as extra input the representation extracted by a deep convolutional
net from an image, with the whole system trained to ``translate''
images into captions. Reproduced from~\citet{Vinyals-et-al-arxiv2014}.
}
\label{fig:caption-generation}
\end{figure}

Similarly, instead of translating the meaning of a French sentence to an English sentence,
one can learn to ``translate'' the meaning of an image into an English sentence,
as illustrated in Figure~\ref{fig:caption-generation}. The ``encoder'' here is
a convolutional neural network (see below), a deep architecture that is particularly
well suited to extract a meaningful representation from an image, while the ``decoder''
is a recurrent neural network similar to the ones used for machine translation
and neural language modeling. There has been a surge of interest in such
systems recently~\citep{Vinyals-et-al-arxiv2014,OTHER-CAPTION-GENERATION-PAPERS}.

@@

\iffalse

@@

\fi

@@

\section{Boxes (TODO)}
